---
title: "Assignment 4"
author: "Jillian Allison, Erica Bishop, Hailey Veirs"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries, message=FALSE}

library(sensitivity)
library(tidyverse)
library(lhs)
library(purrr)
library(ggpubr)
library(viridis)

```

```{r source function}
source("Catm-1.R")

```

## (a) Latin Hypercube Sensitivity Analysis

```{r parameter distribution}

#set seed
set.seed(123)

#number of samples
nsample <- 100

# which parameters
pnames <- c("height", "k_d", "k_o", "v")

# how many parameters
npar <- length(pnames)

#create cube of parameter space
parm_quant <- randomLHS(nsample, npar)
colnames(parm_quant)=pnames #set column names with parameter names

#create a dataframe out of the hyercube
parm <- as_data_frame(matrix(nrow=nrow(parm_quant), ncol=ncol(parm_quant)))
colnames(parm) <- pnames #set column names to parameter names

# set constraints for parameter distributions

#vegetation height distribution
parm[,"height"] <- runif(parm_quant[,"height"],
                         min = 9.5,
                         max = 10.5)

#percent variation for kd and ko
pvar <- 0.01

#kd and k0 distributions
parm[,"k_d"] <- qnorm(parm_quant[,"k_d"],
                     mean = 0.7,
                     sd = 0.7*pvar)
parm[,"k_o"] <- qnorm(parm_quant[,"k_o"],
                     mean = 0.1,
                     sd = 0.1*pvar)

#distribution for windspeed (v)
parm[,"v"] <- qnorm(parm_quant[,"v"],
                    mean = 250,
                    sd = 30)

#check out our data frame of possible parameter values
head(parm)

```
## (b) Run model over parameters

```{r run function}

#use pmap to run functon across our hypercube of parameters

conductance <- parm %>% 
  pmap(Catm) #zm already set as default to 200cm


#check out results
head(conductance)

#turn it into a dataframe
conductance_df <- data.frame(conductance = unlist(conductance,
                                                  use.names = FALSE)) %>% 
  cbind(parm)

```

## (c) Plot conductance accounting for uncertainty

```{r plot conductance}


ggplot(
  data = conductance_df,
  aes(x = conductance)
) +
  geom_density(color = "yellow",
               size = 1,
               fill = "lemonchiffon") +
  theme_minimal() +
  labs(
    x = "Conductance (mm/s)",
    y = "Density",
    title = "Ca Model Conductance (mm/s)"
  )


```


## (d) Plot conductance estimates against parameters

```{r plot uncertainty}

height_plot <-  ggplot(
  data = conductance_df,
  aes(x = height,
      y = conductance,
      col = height)
) +
  geom_point() +
  labs(
    title = "Atmospheric Conductance Sensitivity Analysis"
  ) +
  theme_minimal()

ko_plot <- ggplot(
  data = conductance_df,
  aes(x = k_o,
      y = conductance,
      col = k_o)
) +
  geom_point() +
  scale_color_viridis_c(option = "magma") +
  theme_minimal()

kd_plot <- ggplot(
  data = conductance_df,
  aes(x = k_d,
      y = conductance,
      col = k_d)
) +
  geom_point() +
  scale_color_viridis_c(option = "viridis") +
  theme_minimal()

v_plot <- ggplot(
  data = conductance_df,
  aes(x = v,
      y = conductance,
      col = v)
) +
  geom_point() +
  theme_minimal()

ggarrange(height_plot, ko_plot, kd_plot, v_plot)



```
## (e) Estimate partial rank correlation coefficients 

```{r pcc}

#calculate partial correlation coefficients, ranking them
ca_result <- pcc(parm, conductance_df$conductance, rank = TRUE)

#plot
plot(ca_result)

#make a table of ranked partial correlation coefficients
ca_result


```
## (f) Interpret results

In looking at the results from our sensitivity analysis, wind speed is the parameter that has the strongest relationship with conductance, so the model is the most sensitive to changes in windspeed. In analysis of atmospheric conductance, we may want to control for or adjust for wind speed and any confounding variables. Height also had a relatively high partial rank correlation coefficient, so we'd also want to control for and adjust for that variable in further analysis. 

Based on these results, we can infer that higher windspeeds will create greater atmospheric conductance. Greater atmospheric conductance increases plant water usage. It's tough to say on a global scale how wind speeds will change with climate change, but in areas where climate change is linked to increased wind speeds, we can expect to see plant water usage increasing. 



